---
title: "3explore_functions_dataset"
author: "Noelle Schenk"
date: "April 25, 2019"
output: html_document
---
*note*: 
This file requires the functions dataset `raw_functions` which is constructed in the previous scripts `1read_raw_dataset.Rmd` and `2calc_raw_dataset.Rmd`. It is an example of how to explore missing data and correlations
```{r}
library(naniar)
```

# Missing data
```{r}
vis_miss(raw_functions[, !colnames(raw_functions) %in% c("Explo","Plotn", "Plot"), with=F]) # plot and explo don't contain any missing data
```

```{r}
#USER : set treshold for missing values
treshold <- 0.21
t <- apply(raw_functions, 2, function(x) sum(is.na(x)))
exclude <- names(which(t > 150 * treshold))

small_raw_functions <- raw_functions[, !colnames(raw_functions) %in% exclude, with=F]
```
Visualisation of new situation
```{r}
vis_miss(small_raw_functions[, !colnames(raw_functions) %in% c("Explo","Plotn", "Plot"), with=F])
```


Are there plots which are missing in all variables?
```{r}
gg_miss_upset(small_raw_functions)
```


# Correlations
```{r}
M <- cor(small_raw_functions[, !colnames(raw_functions) %in% c("Explo","Plotn", "Plot"), with=F], use="pairwise.complete.obs")
corrplot::corrplot(M,type="lower",addCoef.col = "black",method="color",diag=F, tl.srt=1, tl.col="black", mar=c(1,0,1,0), number.cex=0.6)
```

Correlations for analysis should not be over a given treshold.
```{r}
treshold <- 0.7
M[M < 0.7 & M > -0.7] <- 0
corrplot::corrplot(M,type="lower", tl.srt=1, tl.col="black", diag = F, title = "Correlations over 0.7",  mar=c(0,0,2,0))
```
High correlations between following variables : 
- ...
add reasons for keeping/ removing them.

